A First Look at Celestial Holography

### 2021-08-07 alpha/CelestialHolography/celestial.tex
Add comments on string partition function & more
Add minor updates to various notes

\section{Basics}
\subsection{\textsl{What} is the celestial sphere?}
	The celestial sphere, \textit{天球}, is a basic concept in astronomy. According to \href{https://en.wikipedia.org/wiki/Celestial_sphere}{\textsl{Wikipedia}}, the celestial sphere is an abstract sphere that has an arbitrarily large radius and is concentric to the observer. All objects in the sky can be conceived as being projected upon the inner surface of the celestial sphere.

@@

	\textsl{We will primarily work in \textbf{4D}, where the celestial spheres are \textbf{2-spheres}}, $CS^\pm \ni (z,\bar{z})$. 
	\begin{equation}
		\dd{s}^2
		= - \dd{u}^2 - 2\dd{u} \dd{r}
			+ r^2 \dd{\Omega}^2,
	\quad
		u = t - r,
	\end{equation}
	\vspace{-.8\baselineskip}
	\begin{equation}
		\dd{\Omega}^2
		= 2\gamma_{z\bar{z}} \dd{z} \dd{\bar{z}},
	\quad
		\gamma_{z\bar{z}}
		= \frac{2}{(1 + z\bar{z})^2}
	\label{eq:metric_null_plus}
	\end{equation}
	$u$: \textbf{retarded time}. 
	These coordinates work well near $\mscr{I}^+$ where $t,r\to\infty$ but $u = t - r$ stays finite. It's no good around $\mscr{I}^-$ where $u\to -\infty$; instead we need \textbf{advanced coordinates}:
	\begin{equation}
		\dd{s}^2
		= - \dd{v}^2
			\mathbin{\sidenote{+}} 2\dd{v} \dd{r}
			+ r^2 \dd{\Omega}^2,
	\quad
		v = t + r,
	\end{equation}
%	\meaning\sidenote

@@

	Now consider a scattering process happening ``around $i^0$'', from $\mscr{I}^-$ to $\mscr{I}^+$; this is ``far away'' from the ``center'' where all the interactions take place, so the scattering process is almost trivial. 
	This gives the natural \textbf{antipodal matching condition} for fields around $i^0$:
	\begin{equation}
		F(u,z,\bar{z})|_{\mscr{I}^+\to i^0}
		= F(u\to -\infty,z,\bar{z})
		\equiv F(z,\bar{z})
		= F(v\to +\infty,z,\bar{z})
		= F(v,z,\bar{z})|_{\mscr{I}^-\to i^0}
	\end{equation}
	Note that this antipodal matching condition will prove crucial to our discussions later on. 
\subsection{\textsl{Why} do we want to study that?}
	\begin{enumerate}
	\item As an approach to \textbf{flat holography}. Another interesting observation: one can do some sort of a ``double holography'' by \textit{uplifting} $\mrm{AdS}_3/\mrm{CFT}_2$; this discussed in e.g.~\cite{deBoer:2003vf,Ball:2019atb}.

@@

		One can implement the \textbf{Euclidean holography} $\mrm{EAdS}_3/\mrm{CFT}_2$ in the red patch, along \textbf{a specific time slice} of the causal future \cite{deBoer:2003vf,Ball:2019atb}. 
		On the other hand, in the blue Rindler patches we can apply Lorentzian $\mrm{dS}_3/\mrm{CFT}_2$.

@@

\pagebreak[4]
	For more on of $\mrm{dS}/\mrm{CFT}$, see\footnote{
		We can read these papers in future journal clubs. Fun facts: just before \citefield{Strominger:2001pn}[eprint:arxivid]{eprint}, we have \arxiv{hep-th/0106112} which is the famous AdS two-sided black hole paper by Maldacena. 
	}:
	\begin{itemize}[noitemsep]
	\item The $\mrm{dS}/\mrm{CFT}$ paper by \textcite{Strominger:2001pn},
	\item Also \textcite{Witten:2001kn},
	\item And Maldacena's comments \textcite{Maldacena:2002vr}. 
	\end{itemize}
	This flavor of $\mrm{dS}/\mrm{CFT}$ is far more ambiguous than the usual $\mrm{AdS}/\mrm{CFT}$ and somewhat ``suspicious''; see Maldacena's comments in \cite{Maldacena:2002vr} and Susskind's recent talk at IAS.

@@

	\begin{figure}[!h]
	\centering
	\includegraphics[width=.7\linewidth]{img/IRtriangle.pdf}
	\caption[The universal IR triangle]{
		The universal IR triangle, modeled after the one in \cite{Strominger:2017zoo}. 
	}
	\end{figure}

@@

	Boundary conditions: suitable choice of asymptotic falloffs and gauge conditions; 
	\begin{equation}
		\mrm{ASG}
		= \frac{
			\textsl{allowed gauge symmetries: repect boundary conditions}
		}{
			\textsl{trivial gauge symmetries: act trivially on boundary data (charges)}
		}
	\end{equation}
	e.g.~In asymptotically flat 4D gravity, if we restrict to Lorentz plus ``small translations'', we obtain $\mrm{BMS}_4 = \mrm{BMS}^+ \times \mrm{BMS}^- \supset \mrm{Poincar\'e}$, i.e.~it is \textbf{$\infty$-ly larger} than the isometry of Minkowski!

@@

\appendix
\section{Symmetries of asymptotically flat spacetime}
	\vspace{-.5\baselineskip}
	\begin{center}
	\includegraphics[width=.635\linewidth]{img/ASGflat.pdf}
	\end{center}

>>>>

\section{Basics}
\subsection{\textsl{What} is the celestial sphere?}
	The celestial sphere, \textkai{天球}, is a basic concept in astronomy. According to \href{https://en.wikipedia.org/wiki/Celestial_sphere}{\textsl{Wikipedia}}, the celestial sphere is an abstract sphere that has an arbitrarily large radius and is concentric to the observer. All objects in the sky can be conceived as being projected upon the inner surface of the celestial sphere.

@@

	\textsl{We will primarily work in \textbf{4D}, where the celestial spheres} $CS^\pm \simeq S^2 \ni (z,\bar{z})$. 
	\begin{equation}
		\dd{s}^2
		= - \dd{u}^2 - 2\dd{u} \dd{r}
			+ r^2 \dd{\Omega}^2,
	\quad
		u = t - r,
	\end{equation}
	\vspace{-.8\baselineskip}
	\begin{equation}
		\dd{\Omega}^2
		= 2\gamma_{z\bar{z}} \dd{z} \dd{\bar{z}},
	\quad
		\gamma_{z\bar{z}}
		= \frac{2}{(1 + z\bar{z})^2}
	\label{eq:metric_null_plus}
	\end{equation}
	$u$: \textbf{retarded time}. 
	These coordinates work well near $\mscr{I}^+$ where $t,r\to\infty$ but $u = t - r$ stays finite. It's no good around $\mscr{I}^-$ where $u\to -\infty$; instead we need \textbf{advanced coordinates}:
	\begin{equation}
		\dd{s}^2
		= - \dd{v}^2
			\mathbin{\sidenote{+}} 2\dd{v} \dd{r}
			+ r^2 \dd{\Omega}^2,
	\quad
		v = t + r,
	\end{equation}
%	\meaning\sidenote

@@

	Now consider a scattering process happening ``around $i^0$'', from $\mscr{I}^-$ to $\mscr{I}^+$; this is ``far away'' from the ``center'' where all the interactions take place, so the scattering process is almost trivial. 
	This gives the natural \textbf{antipodal matching condition} for fields around $i^0$:
	\begin{equation}
	\arraycolsep=.25em
	\begin{array}{ccccccccc}
		F(u,z,\bar{z})|_{\mscr{I}^+\to i^0}
		&=& F(u\to -\infty,z,\bar{z})
		&\equiv& F(z,\bar{z})
		&=& F(v\to +\infty,z,\bar{z})
		&=& F(v,z,\bar{z})|_{\mscr{I}^-\to i^0}
	\end{array}
	\end{equation}
	Note that this antipodal matching condition will prove crucial to our discussions later on. 
\subsection{\textsl{Why} do we want to study that?}
	\begin{enumerate}
	\item As an approach to \textbf{flat holography}. Another interesting observation: one can do some sort of a ``double holography'' by \textit{uplifting} $\mrm{AdS}_3/\mrm{CFT}_2$; this discussed in e.g.~\cite{deBoer:2003vf,Ball:2019atb}.

@@

		One can implement the \textbf{Euclidean holography} $\mrm{EAdS}_3/\mrm{CFT}_2$ in the red patches, along \textbf{a specific time slice} of the causal future \cite{deBoer:2003vf,Ball:2019atb}. 
		On the other hand, in the blue Rindler patches we can apply Lorentzian $\mrm{dS}_3/\mrm{CFT}_2$.

@@

\pagebreak[4]
	For more on of $\mrm{dS}/\mrm{CFT}$, see\footnote{
		We can read these papers in future journal clubs. Fun facts: just before \citefield{Strominger:2001pn}[eprint:arxivid]{eprint}, we have \arxiv{hep-th/0106112} which is the famous AdS two-sided black hole paper by Maldacena. 
	}:
	\begin{itemize}[noitemsep]
	\item The $\mrm{dS}/\mrm{CFT}$ paper by \textcite{Strominger:2001pn},
	\item Also \textcite{Witten:2001kn},
	\item And Maldacena's comments: \citefield{Maldacena:2002vr}[eprint:arxivid]{eprint}~\cite{Maldacena:2002vr}. 
	\end{itemize}
	This flavor of $\mrm{dS}/\mrm{CFT}$ is far more ambiguous than the usual $\mrm{AdS}/\mrm{CFT}$ and somewhat ``suspicious''; see Maldacena's comments in \cite{Maldacena:2002vr} and Susskind's recent talk at IAS.

@@

	\begin{figure}[!h]
	\centering
	\includegraphics[width=.85\linewidth]{img/IRtriangle.pdf}
	\caption[The universal IR triangle]{
		The universal IR triangle, modeled after the one in \cite{Strominger:2017zoo}. 
	}
	\end{figure}

@@

	Boundary conditions: suitable choice of asymptotic falloffs and gauge conditions; 
	\begin{equation}
		\mrm{ASG}
		= \frac{
			\textsl{allowed gauge symmetries: repect boundary conditions}
		}{
			\textsl{trivial gauge symmetries: act trivially on boundary data (charges)}
		}
	\end{equation}
	e.g.~In asymptotically flat 4D gravity, if we restrict to Lorentz plus ``small translations'', we obtain $\mrm{BMS}_4 = \mrm{BMS}^+ \times \mrm{BMS}^- \supset \text{Poincar\'e}$, i.e.~it is \textbf{$\infty$-ly larger} than the isometry of Minkowski!

@@

\appendix
\section{Symmetries of asymptotically flat spacetime}
	\vspace{-.5\baselineskip}
	\begin{center}
	\includegraphics[width=.85\linewidth]{img/ASGflat.pdf}
	\end{center}
